Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-10 methods_paper/fabl-paper.tex
minor change to abstract. great job bk.

{
	\color{blue} Thanks Beka for writing that first abstract. I think this one captures the idea better, even if its not exactly in "outline" form.
	\vspace{1em}
}

In this paper, we propose \emph{fast beta linkage} (\texttt{fabl}), which extends a recent Bayesian Fellegi Sunter model for increased efficiency and scalability. Specifically, we relax the one-to-one matching requirement of the Beta Record Linkage method of \citep{sadinle_bayesian_2017} and propose independent priors over the matching space. This allows us to employ hashing techniques that hasten calculations and reduce computational complexity, complete pairwise record comparisons over large datasets through parallel computing, and reduce memory costs through a new technique called \emph{storage efficient indexing}. Through simulation studies and a case study of homicides from the El Salvadoran Civil War, we show that our method has markedly increased speed with minimal loss of accuracy.

>>>>

%{
%	\color{blue} Thanks Beka for writing that first abstract. I think this one captures the idea better, even if its not exactly in "outline" form.
%	\vspace{1em}
%}

In this paper, we propose the \emph{fast beta linkage} method (\texttt{fabl}), which extends a recent Bayesian Fellegi Sunter model for increased efficiency and scalability. Specifically, we relax the one-to-one matching requirement of the Beta Record Linkage method of \citep{sadinle_bayesian_2017} and propose independent priors over the matching space. This allows us to employ hashing techniques that hasten calculations and reduce the overall computational complexity. In addition, we are able to complete pairwise record comparisons over large datasets through parallel computing and reduce memory costs through a new technique called \emph{storage efficient indexing}. Through simulation studies and a case study of homicides from the El Salvadoran Civil War, we show that our method has markedly increased speed with minimal loss of accuracy. Finally, we discuss our work and future directions.
